\documentclass[a4paper]{report}
\usepackage{unifrrr}
\usepackage{graphicx}
\usepackage[latin1]{inputenc}
\usepackage{float}
\usepackage[colorlinks=false, pdfborder={0 0 0}]{hyperref}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{bibgerm}
\usepackage[english]{babel}
\usepackage{listings}
\usepackage{color}
\usepackage{appendix}
\usepackage{minitoc}
\usepackage[onehalfspacing]{setspace}
\usepackage[nottoc]{tocbibind}
\usepackage{multirow}
\usepackage{longtable}
\definecolor{javared}{rgb}{0.6,0,0} % for strings
\definecolor{javagreen}{rgb}{0.25,0.5,0.35} % comments
\definecolor{javapurple}{rgb}{0.5,0,0.35} % keywords
\definecolor{javadocblue}{rgb}{0.25,0.35,0.75} % javadoc


\lstset{language=Java,
basicstyle=\ttfamily\footnotesize,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
morecomment=[s][\color{javadocblue}]{/**}{*/},
numbers=left,
numberstyle=\tiny\color{black},
stepnumber=1,
numbersep=10pt,
tabsize=4,
showspaces=false,
showstringspaces=false,
captionpos=b}

\begingroup
    \catcode `\@ = 11
    \catcode `\~ = 13
    \catcode `\% = 12
    \protected\long\gdef\cmt@remove#1%~{\endgroup}
    \ifdefined~
        \global\let\cmt@old~
    \else
        \global\let\cmt@old\relax
    \fi
    \protected\gdef~{\begingroup\catcode`%=12
        \futurelet\next\cmt@}
    \protected\gdef\cmt@
      {\ifx%\next
           \expandafter\cmt@remove
       \else
           \endgroup\expandafter\cmt@old
       \fi}
\endgroup


\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

%--------------------------------------------------------------------


%The body of the LaTeX file
\begin{document}  



%Including of the title page. See titlepage.tex file
\include{tex/titlepage}

\pagenumbering{arabic}
\pagestyle{plain}
\newpage

\include{tex/declaration}
\include{tex/acknowledgements}
\include{tex/abstract}

\dominitoc
\tableofcontents
\newpage

\listoffigures

\listoftables

\lstlistoflistings

\chapter{Introduction}
eBay Inc.\footnote{http://www.ebay.com} is one of the world's largest online marketplaces and reported 128 million active users worldwide during the last quarter of the year 2013. Online auction platforms make consumer-to-consumer transactions possible. The seller can present articles by uploading pictures and characterise them by writing proper descriptions. The creation of an auction is time consuming and needs a lot of investigations. Searching for descriptions on the internet or finding a selling price for the same or similar article, for example. In 2005, Jeff Howe and Mark Robinson created a term called 'Crowdsourcing' which is a combination of the words crowd and outsourcing. The idea behind the term is to outsource different tasks, which are difficult to solve by machines, to the crowd. To reduce the costs of collecting information for an article to sell on an auction platform, tasks will be created and outsourced to the crowd. Amazon Mechanical Turk\footnote{http://www.mturk.com}, short MTurk, is a crowdsourcing marketplace which enables requesters to publish human intelligence tasks (HITs). The workers can solve these tasks and earn money for their work.

\section{Statement of the Problem}
The first step of creating an online auction is mostly to take pictures of the item. This helps the buyers to get information about the state and quality of the article. After that the item needs a short and clear description, some properties (category, state) and a starting bid. If the seller wants to create a lot of different auctions, the whole procedure is time consuming and boring. A price estimation of an article can be difficult, because the background knowledge is missing and other auctions to compare aren't available at any time. Machines aren't able to solve all these steps by them self, because the spectrum of the articles is huge and image processing methods aren't capable to classify all of them correctly. To get all the needed parts of an online auction, a human powered approach is necessary. Crowdsourcing platforms provide the possibility to solve tasks which are difficult to handle for a computer.

\section{Existing Research}
Some similar existing research projects will be illustrated in this section: 
\subsection{Crowdsourcing}
The idea of the thesis is similar to a project called ``PlatMate''\cite{platemate} where workers analyse the content of food photographs. The processing pipeline consists of three major steps and put out the calorie values of every ingredient on the picture. All steps were performed by workers of a crowdsourcing platform. The accuracy of the calorie estimations of the system was almost as good as estimations from different trained experts. 
\subsection{Price Estimation}
The vision of predicting the end price of online auctions is not new. People from the Accenture Technology Labs\footnote{http://www.accenture.com} tried to do this in 2005 and published some surprising results\cite{ghani}. They collected 1'700 auctions of a specific item, during a two-month period, to form a training and test set. The end prices of the ground truth are additionally converted to a price class (10\% of the average price) to perform classification algorithms. The accuracy of the classifiers are higher then 70\%.

\section{Goals and Objectives}
The thesis has the following goals and their corresponding objectives:
\begin{itemize}
	\item \textbf{Collect auction item properties by the crowd}
	\begin{itemize}
		\item Analyse the composition of an auction item on eBay and select the parts which can be crowdsourced
		\item Form a ground truth including different auctions created by real online auction platform users by using the eBay API
		\item Study literature which covers similar crowdsourcing problems
		\item Design and publish tasks on Amazon Mechanical Turk to gather data from the crowd
		\item Evaluate the quality of the generated contents
	\end{itemize}
	\item \textbf{Vary the design of the tasks and investigate the behaviour of the workers}
	\begin{itemize}
		\item Find parameters for the HITs
		\item Analyse the influence on the performance of the workers
	\end{itemize}
	\item \textbf{Try to improve the initial solution by implementing a hybrid approach}
	\begin{itemize}
		\item Search for image processing or machine learning methods which can simplify and/or support a human intelligence task
		\item Implement the methods and adapt the design of the tasks
	\end{itemize}
\end{itemize}

\section{Organisation}
The thesis report is organised in multiple chapters. At the beginning of the document, the eBay marketplace and the corresponding API will be investigated (Chapter \ref{chap:ebay}). Then the theoretical background knowledge about crowdsourcing is summarised (Chapter \ref{chap:crowdsourcing}). The learned theory was used to build up a workflow to generate online auction contents (Chapter \ref{chap:implementation}). The observations of the executed experiments are concluded in the next chapter (Chapter \ref{chap:evaluation}). The results of the thesis are discussed in the next-to-last chapter of the report (Chapter \ref{chap:discussion}). Some ideas for improvements and a summary of the pros and cons of the implemented approach are part of the last chapter (Chapter \ref{chap:conclusion}). All the ground truth items, some plots and tables which haven't find a place in the report are listed in the appendix section.

\chapter{eBay Online Marketplace}
\label{chap:ebay}
\include{tex/marketplace}

\chapter{Crowdsourcing}
\label{chap:crowdsourcing}
\include{tex/crowdsourcing}

\chapter{Implementation}
\label{chap:implementation}
\include{tex/implementation}

\chapter{Evaluation}
\label{chap:evaluation}
\include{tex/evaluation}

\chapter{Discussion}
\label{chap:discussion}
\include{tex/discussion}

\chapter{Conclusion}
\label{chap:conclusion}
\include{tex/conclusion}

\clearpage

\selectlanguage{english}
\bibliographystyle{bib/custom}
\bibliography{bib/references}
\newpage
\begin{appendices}
\include{tex/appendices}
\end{appendices}

\end{document}
